---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gdphelperR

<!-- badges: start -->
[![R-CMD-check](https://github.com/UBC-MDS/gdphelperR/workflows/R-CMD-check/badge.svg)](https://github.com/UBC-MDS/gdphelperR/actions)
<!-- badges: end -->

The goal of gdphelperR is to take the url of any of the several dozen GDP-related csv datasets from the [Canadian Government Open Data Portal](https://open.canada.ca/en/open-data) and download, clean load, summarize and visualize the data contained within.

## Installation

You can install the released version of gdphelperR from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("gdphelperR")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("UBC-MDS/gdphelperR")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(gdphelperR)
## basic example code
```

## Usage

- TODO

## Contributors

- Aldo Barros          aldosaltao@gmail.com
- Gabe Fairbrother     gfairbrother@gmail.com
- Wanying Ye           wanying.ye2020@gmail.com
- Ramiro Mejia         ramiromejiap@gmail.com

## Contributing

Interested in contributing? Check out the [contributing guidelines](https://github.com/UBC-MDS/Group_03_GOV_CA_GDP_HELPER/blob/main/CONTRIBUTING.md). 

## Code of Conduct

Please note that the gdphelperR project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## License

`gdphelperR` was created by Aldo Barros, Gabriel Fairbrother, Ramiro Mejia, Wanying Ye. It is licensed under the terms of the MIT license.
