---
title: "Welcome to gdphelperR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{gdphelperR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(gdphelperR)
```

First of all, let's retrieve a GDP-related data set from Open Government Portal using `gdpimporterr`. The first element of the output from `gdpimporterr` is the data frame which can be used for downstream data wrangling and analysis, while the second element is a character vector containing the title information from the MetaData. 

```{r}
# Use gdpimporterr to download and import data
raw_data <- gdpimporterr("https://www150.statcan.gc.ca/n1/tbl/csv/36100400-eng.zip")
knitr::kable(head(raw_data[[1]]))
raw_data[[2]]
```

Then, `gdpcleanerr` helps to rename the column names and clean up the useless columns, preparing the data for summary statistics (`gdpdescriberr`) and visualization (`gdpploterr`).

```{r}
# Use gdpcleanerr to clean raw data
clean_data <- gdpcleanerr(raw_data[[1]])
knitr::kable(head(clean_data))
```

`gdpdesciberr` is used to produce customized statistics summary in a nice and easy format.

```{r}
# Use gdpdescriberr to produce basic summary statistics
stats <- gdpdescriberr(clean_data, Value, Location, .stats=c("mean", "sd", "max"), dec = 3)
knitr::kable(stats)
```

Finally, `gdpimporterr` gives a line plot for GDP values across provinces. 

```{r plot, fig.width=8, fig.height=8, fig.cap="Figure 1. Line plot for GDP for provinces in Canada"}
# Use gdpplotterr to produce a plot 
gdpplotterr(clean_data)
```

